%-------------------------------------
% Professional Resume - Clean Design
% Author: David Bałut
%------------------------------------

\documentclass[10pt, letterpaper]{article}

% Packages
\usepackage[top=0.5in, bottom=0.5in, left=0.8in, right=0.8in]{geometry}
\usepackage{enumitem}
\usepackage{hyperref}
\usepackage{tabularx}

% Hyperlink setup
\hypersetup{
    colorlinks=true,
    linkcolor=black,
    urlcolor=black,
}

% Remove paragraph indentation
\setlength{\parindent}{0pt}

% Section formatting
\usepackage{titlesec}
\titleformat{\section}
  {\vspace{-4pt}\scshape\raggedright\large}
  {}
  {0em}
  {}
  [\titlerule \vspace{-5pt}]

% --------------------  START  --------------------
\begin{document}

% -------------------- HEADING --------------------
\vspace{-20pt}
\begin{center}
    {\LARGE \textbf{David Bałut}} \\
    \vspace{2pt}
    224-636-6796 $\cdot$ \href{mailto:davidbalut@gmail.com}{davidbalut@gmail.com} $\cdot$ \href{https://scholar.google.com/citations?user=3pZLDeAAAAAJ&hl=en&oi=ao}{\textcolor{blue}{\underline{Google Scholar}}} $\cdot$ \href{https://david-balut.github.io}{\textcolor{blue}{\underline{Personal Website}}}
\end{center}

% -------------------- EDUCATION --------------------
\section{Education}
\begin{tabularx}{\textwidth}{X r}
\textbf{University of Cambridge} & Cambridge, United Kingdom \\
MPhil in Physics & September 2026 -- 2027 \\
\end{tabularx}
\vspace{4pt}
\begin{tabularx}{\textwidth}{X r}
\textbf{University of Illinois, Grainger College of Engineering} & Urbana, Illinois \\
B.S. in Physics, Minor in Mathematics & 2022 -- May 2026 \\
\end{tabularx}
\vspace{2pt}
\begin{itemize}[leftmargin=20pt, topsep=0pt, itemsep=2pt]
\item[] GPA: 4.00/4.00
\end{itemize}

% -------------------- PUBLICATIONS --------------------
\section{Publications}
\vspace{2pt}
\begin{enumerate}[leftmargin=20pt, topsep=0pt, itemsep=4pt]

\item \textbf{David Bałut}, Barry Bradlyn, Peter Abbamonte. ``Quantum entanglement and quantum geometry measured with inelastic X-ray scattering.'' \textit{Phys. Rev. B} \textbf{111}, 125161 (2025). DOI: 10.1103/PhysRevB.111.125161 (Editor's Suggestion)

\item \textbf{David Bałut}, Xuefei Guo, Niels de Vries, Dipanjan Chaudhuri, Barry Bradlyn, Peter Abbamonte, Philip W. Phillips. ``Quantum Fisher Information Reveals UV-IR Mixing in the Strange Metal.'' \textit{Physica C: Superconductivity and its Applications} \textbf{635}, 1354750 (2025). DOI: 10.1016/j.physc.2025.1354750

\item \textbf{David Bałut}, Barry Bradlyn, Marcus D. Collins, Peter Abbamonte. ``Fundamental Tests of Quantum Geometric Bounds in Ionic and Covalent Insulators using Inelastic X-Ray Scattering.'' \href{https://arxiv.org/abs/2601.19054}{arXiv:2601.19054} (2026).

\item N. de Vries, E. Hoglund, D. Chaudhuri, J. Chen, X. Guo, \textbf{D. Bałut}, G. Gu, P. Huang, J. Hachtel, P. Abbamonte. ``Reexamining the strange metal charge response with transmission inelastic electron scattering.'' arXiv:2602.02348 (2026).

\item C. Bernal-Choban, D. Chaudhuri, \textbf{D. Bałut}, A. Chakraborty, T. Su, Y. Cai, E. Ertekin, T-C. Chiang, R. Fernandes, P. Abbamonte. ``Anomalous structural fluctuations near the spin order transition in the candidate altermagnet MnF$_2$.'' (In preparation for \textit{Phys. Rev. Lett.})

\item \textbf{D. Bałut}, B. Bradlyn, P. Abbamonte. ``Electronic Entanglement of Insulators Measured with Inelastic X-ray Scattering.'' (In preparation for \textit{Nature})

\end{enumerate}

% -------------------- CONFERENCE PRESENTATIONS --------------------
\section{Conference Presentations}
\vspace{2pt}
\begin{itemize}[leftmargin=20pt, topsep=0pt]
\item \textit{APS March Meeting}, Denver, CO, March 2026.
\item \textit{Gulf Coast Undergraduate Research Symposium}, Rice University, Houston, TX, Oct 18, 2025.
\item \textit{Astronaut Scholarship Foundation Technical Conference}, Houston, TX, Aug 16, 2025.
\item \textit{APS March Meeting}, Anaheim, CA, March 18, 2025.
\end{itemize}

% -------------------- AWARDS & HONORS --------------------
\section{Awards and Honors}
\vspace{2pt}
\begin{tabularx}{\textwidth}{X r}
\textbf{Churchill Scholar} & February 2026 \\
\textit{Fellowship for graduate study at the University of Cambridge (15 awarded nationwide)} & \\
\textit{Winston Churchill Foundation of the United States} & \\[4pt]

\textbf{Astronaut Scholar} & May 2025 \\
\textit{National scholarship for STEM undergraduates (74 awarded nationwide)} & \\
\textit{The Astronaut Scholarship Foundation} & \\[4pt]

\textbf{Barry Goldwater Scholar} & March 2025 \\
\textit{National scholarship for STEM undergraduates (441 awarded nationwide)} & \\
\textit{The Barry Goldwater Scholarship and Excellence in Education Foundation} & \\[4pt]

\textbf{Paul A Jursinic Engineering Physics Scholarship} & May 2025 \\
\textit{Department of Physics, University of Illinois} & \\[4pt]

\textbf{A.C. Anderson Research Scholar} & May 2024 \\
\textit{Department of Physics, University of Illinois} & \\
\end{tabularx}

\end{document}
